%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 2.0 (6/7/2019)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{article} % Default document font size

\input{structure.tex} % Include the file specifying the document structure and styling

% Set PDF meta-information
\hypersetup{
	pdftitle={João Lourenço - Curriculum vitae},
	pdfauthor={João Lourenço}
}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION
%----------------------------------------------------------------------------------------

{\LARGE\bfseries João LOURENÇO} % Name
\bigskip\bigskip\medskip % Whitespace

Max-Planck-Institut für Mathematik\\ % Address
 Bonn, Germany
\medskip % Whitespace

%Phone: 609-734-8000\\ % Phone number
%Mobile: 609-924-8399 % Mobile number
%\medskip % Whitespace

E-mail: \href{mailto:lourenco@mpim-bonn.mpg.de}{lourenco@mpim-bonn.mpg.de}\\ % Email address
\textsc{url}: \href{https://rastrel.github.io/Lourenco/}{webpage}\\ % Academic/personal website

%\vspace{0.04\textheight} % Whitespace between contact information and specific CV information

%------------------------------------------------

%Né le 27 avril 1994 à Porto, Portugal\\ % Date of birth
%Nationalité: Portugaise % Nationality

%------------------------------------------------

 % Current or most recent employment position

%------------------------------------------------

\section*{Research}

Mathematics ; Arithmetic geometry ; Shimura varieties, Langlands program, and geometric representation theory. % Primary areas of research interest

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section*{Employment}

 \emph{Wissenschaftlicher Mitarbeiter}, \years{2022-25}Westfälische Wilhelms-Universität Münster. \\

 \emph{Gast},\years{2022} Max-Planck-Institut für Mathematik, Bonn. \\

\emph{Research associate},\years{2020--21} Imperial College London \\

\emph{Wissenschaftlicher Mitarbeiter}, Rheinische\years{2017--20} Friedrich-Wilhelms-Universität Bonn

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section*{Education}
BSc\years{2015} in Mathematics, Faculdade de Ciências da Universidade do Porto\\

MSc\years{2017} in Mathematics, Rheinische Friedrich-Wilhelms-Universität Bonn \\ Advisor: Prof. Dr. Peter Scholze \\

PhD\years{2020} in Mathematics, Rheinische Friedrich-Wilhelms-Universität Bonn \\ Advisor: Prof. Dr. Peter Scholze
%----------------------------------------------------------------------------------------
%	GRANTS, HONOURS AND AWARDS
%----------------------------------------------------------------------------------------

%\section*{Grants, honours \& awards}

%\years{1921}Nobel Prize in Physics, Nobel Foundation

%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS
%----------------------------------------------------------------------------------------

\section*{Production}


 ``The\years{2017} Riemannian Hebbarkeitssätze for pseudo-rigid spaces'', \href{https://arxiv.org/abs/1711.06903}{arXiv:1711.06903}.  \\

 ``Grassmanniennes\years{2019} affines tordues sur les entiers'', \href{https://arxiv.org/abs/1912.11918}{arXiv:1912.11918}, submitted.\\

``Théorie de Bruhat--Tits pour les groupes quasi-réductifs'',\years{2020} \href{https://arxiv.org/abs/2001.05362}{arXiv:2001.05362}, \emph{Journal de l'Institut de Mathématiques de Jussieu}, \href{https://www.cambridge.org/core/journals/journal-of-the-institute-of-mathematics-of-jussieu/article/abs/theorie-de-bruhattits-pour-les-groupes-quasireductifs/324841C8B4D5E790CB9CBE984D32B13B}{Cambridge University Press}.\\

 ``Théorie de Bruhat--Tits, grassmanniennes affines et modèles locaux'', \years{2020}Dissertation. \emph{Landesbibliothek Uni Bonn}, \href{https://bonndoc.ulb.uni-bonn.de/xmlui/handle/20.500.11811/8641}{bonndoc}.\\

  ``On the normality\years{2020} of Schubert varieties: remaining cases in positive characteristic'', with T. Haines and T. Richarz, \href{https://arxiv.org/abs/1806.11001}{arXiv:1806.11001}, submitted.\\

``On the p-adic\years{2022} theory of local models'', with J. Anschütz, I. Gleason, and T. Richarz, \href{https://arxiv.org/abs/2201.01234}{arXiv:2201.01234}, submitted.\\

``Tubular \years{2022}neighborhoods of local models'', with I. Gleason, \href{https://arxiv.org/abs/2204.05526}{arXiv:2204.05526}, submitted.  \\

 ``Singularities \years{2022}of local models'', with N. Fakhruddin, T. Haines, and T. Richarz, \href{https://arxiv.org/abs/2208.12072}{arXiv:2208.12072}. \\


``Gaitsgory's central \years{2022}functor and the Arkhipov--Bezrukavnikov equivalence in mixed characteristic'', with J. Anschütz, Z. Wu, and J. Yu. In preparation. \\

``A modular ramified \years{2022} Satake equivalence'', with P. Achar, T. Richarz, and S. Riche. In preparation. 

%------------------------------------------------


\section*{Talks}
``TBD'', \years{10.23} 75th anniversary of M. Rapoport, Münster.\\

``TBD'', \years{7.23} Local Langlands and p-adic methods, Bonn.\\

``Modèles locaux p-adiques : géométrie'', \years{08.06.22} Paris-Nord.\\

``Modèles locaux p-adiques : cohomologie'', \years{01.06.22} Paris-Nord.\\

``Mini-cours sur la théorie p-adique \years{26.05.22}des modèles locaux'', Caen.
\\

``Tubular neighborhoods of local models II'' \years{06.05.22}, Bonn.\\

``Local models for p-adic shtukas'' \years{28.04.22}, MPI-Oberseminar, Bonn.\\

``On the p-adic \years{15.03.22} theory of local models'', Hong Kong.
\\

``On the p-adic \years{09.02.22} theory of local models II'', Rampage.
\\

``On the p-adic \years{12.01.22} theory of local models '', München.
\\


``Sur la \years{07.12.21} théorie p-adique des modèles locaux'', Orsay.
\\

``Sur la \years{29.11.21} théorie p-adique des modèles locaux'', Paris Rive Gauche.
\\

 ``On the p-adic\years{26.10.21} theory of local models'', Fields Medal Symposium, Toronto.
\\

``Towards \years{11.11.20}the Scholze--Weinstein conjecture on local models'', London.
\\

 ``Vers la conjecture\years{09.10.20} de Scholze--Weinstein sur les modèles locaux'', Paris Nord.
\\

 ``On the \years{24.07.20}geometry of mixed characteristic affine Grassmannians'', Oberwolfach.
\\

``Twisted \years{28.11.19}affine Grassmannians in wildly ramified cases'', Bonn.
\\

``Bruhat--Tits theory \years{21.11.19}for pseudoreductive groups'', Bonn.
\\

 ``Twisted affine Grassmannians \years{21.10.19}over $\mathbf{Z}$'', Modularity and Moduli Spaces, Oaxaca. 
\\

 ``Twisted affine Grassmannians \years{11.10.19}and local models of Shimura varieties'', London.
\\

 ``Twisted Kac-Moody groups \years{30.08.19}over the integers'', Luminy. 
\\

 ``Local models \years{20.12.18}for some wildly ramified groups'', Bonn.  
\\

 ``The Riemannian \years{27.04.17}Hebbarkeitssatz for pseudo-rigid spaces II'', Bonn.  
\\

 ``The Riemannian Hebbarkeitssatz \years{20.04.17}for pseudo-rigid spaces I'', Bonn.  	 

\section*{Conferences}

``Conference on the occasion of Michael Rapoport's 75th birthday'' \years{10.23} Münster, Germany (speaker).\\

``Local Langlands and p-adic methods'' \years{07.23} Bonn, Germany (speaker).\\

``Arithmetic of Shimura varieties'' \years{01.23}, Oberwolfach, Germany (speaker, probably). \\

`` Summer School on The Langlands Programme'' \years{07.22}, Paris, France. \\

``30e Rencontres arithmétiques de Caen'' \years{05.22}, Caen, France (speaker). \\

``2021 Fields Medal Symposium: Peter Scholze'', \years{11.21} Toronto, Canada (speaker). \\

``Oberwolfach Arithmetic Geometry''\years{07.21}, Oberwolfach, Germany (speaker).\\

``Modularity and moduli spaces'',\years{10.19} Oaxaca, Mexico (speaker). \\
 
 ``Hausdorff School on the Emerton-Gee stack and related topics'',\years{08.19} Bonn, Germany. \\
 
``Immeubles et grassmanniennes affines'', \years{09.19} Luminy, France (speaker). \\

``Arithmetic Geometry in Carthage'',\years{06.19} Cartaghe, Tunisia. \\

``The p-adic Langlands programme and related topics'',\years{05.19} London, England.\\

``Groupes algébriques et géométrisation du programme de Langlands''\years{06.18}, Lyon, France. \\

``Leçons Hadamard par P. Scholze''\years{04.17}, Paris, France. \\

``Arizona Winter School 2017: Perfectoid Spaces''\years{03.17}, Tucson, USA.\\

``Oberwolfach Seminar on Perfectoid Spaces''\years{10.16}, Oberwolfach, Germany.


\section*{Seminars}

Arbeitsgemeinschaft ``Bezrukavnikov'',\years{Fall 22} with K. Zou.\\

Seminar ''Darstellungstheorie \years{Fall 22} endlicher Gruppen'', with E. Viehmann. \\

  London NT study group \years{Fall 20}``Geometrization of the Langlands program'', with M. Tamiozzo. \\


\iffalse
 ARGOS \years{hiver 19}``Prismatic Dieudonné theory''\\
Exposé: {\it Finite group schemes over perfectoid rings and $p$-divisible groups over regular rings}\\

 ARGOS ``Wei Zhang's proof of the arithmetic fundamental Lemma''\years{été 19}\\
Exposé: {\it Kudla--Rapoport divisors} \\

 ARGOS ``Prismatic cohomology''\years{hiver 18}\\
Exposé: {\it André's lemma} \\

 ARGOS \years{été 18}``The geometric Satake equivalence for the de Rham affine Grassmannian''\\
Exposé: {\it Affine flag varieties and local models} \\

 ARGOS \years{hiver 17}``Cycles on Shimura varieties via geometric Satake''\\
Exposé: {\it Correspondence between Shimura varieties and cycle classes of the basic locus} \\

 ARGOS \years{été 17}``Sheaves on the stack of vector bundles on the Fargues--Fontaine curve''\\
Exposé: {\it Families of vector bundles II}\\

 ARGOS \years{hiver 16}``Étale cohomology of diamonds''
\fi

\section*{Visits}
Grenoble\years{July 22}, with P. Achar and S. Riche.\\

 Paris-Nord\years{June 22}, with S. Morra and A.-C. Le Bras. \\

 Paris-Saclay\years{Fall 21}, with K. \v{C}esnavi\v{c}ius. \\

 Imperial\years{Feb 20} College London, with A. Caraiani.\\

 Jussieu, with\years{Dec 18} J. Anschütz and T. Richarz.
\section*{Referee}
Annals of Mathematics, Mathematische Annalen, Representation theory, Canadian Journal of Mathematics, Épijournal de Géométrie Algébrique

\section*{Languages}
Portugais (native), French, English, German, Spanish (fluent), Italian (conversational).

\section*{References}

Ana Caraiani, Thomas Haines, Timo Richarz, Peter Scholze
 
%---------------------------------------------------------- ------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------

%\section*{Teaching}

%\ldots

%------------------------------------------------

%\section*{Service to the profession}

%\ldots

\vfill % Whitespace before final footer

%----------------------------------------------------------------------------------------
%	FINAL FOOTER
%----------------------------------------------------------------------------------------

% Any final footer text such as a URL to the latest version of this CV, last updated date, compiled in XeTeX, etc
\begin{center}
	\scriptsize
	Last updated: \today
	%~~\raisebox{-0.5pt}{\textbullet}~~\href{https://www.LaTeXTemplates.com}{https://www.LaTeXTemplates.com}
\end{center}

%----------------------------------------------------------------------------------------

\end{document}
